working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect

### 2018-12-12 Manuscript_draft/Manuscript_draft.Rmd
some changes

1.	 What are the implications of the findings?

@@

Small pollen can clogg the stigma. YES. Big pollen doesn't fit in very small stigmas. YES.

Is small pollen likely to affect bigger pollen. Ideas: It can be compensated with, less number of ovules to fertilize and faster pollen tube growth. So generally speaking, when the differences in pollen size are evident we expect a similar outcome.

>>>>

 What are the implications of the findings?

@@

1) Donor pollen size < Recipient pollen size

*Negative*

-Stigma clogging

-

### 2018-12-12 Manuscript_draft/Manuscript_draft.tex
some changes

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  What are the implications of the findings?
\end{enumerate}

@@

Small pollen can clogg the stigma. YES. Big pollen doesn't fit in very
small stigmas. YES.

Is small pollen likely to affect bigger pollen. Ideas: It can be
compensated with, less number of ovules to fertilize and faster pollen
tube growth. So generally speaking, when the differences in pollen size
are evident we expect a similar outcome.

>>>>

What are the implications of the findings?

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Donor pollen size \textless{} Recipient pollen size
\end{enumerate}

\emph{Negative}

-Stigma clogging

\begin{itemize}
\item
\end{itemize}
